Word2vec learns effective distance of scientific co-affiliation

### 2020-01-27 paper/current/main.tex
Added formatting for supporting information
Added descriptive supporting figure showing reverse cdf of #affiliations by geo scale

@@

\newpage
\section{Supporting Information}

%
% Figure - gravity correlation
%
\begin{figure}[hp!]
	\centering
	\label{fig:projection}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
		\textbf{a.}
		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
	}
\end{figure}

\printbibliography{}

>>>>

% define a command to setup the format of supporting infomration figures and tables. 
% source: http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
\newcommand{\beginsupplement}{%
        \setcounter{table}{0}
        \renewcommand{\thetable}{S\arabic{table}}%
        \setcounter{figure}{0}
        \renewcommand{\thefigure}{S\arabic{figure}}%
     }

@@

\newpage
\section{Supporting Information}
\beginsupplement

%
% Figure - reverse CDF by scale
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:rcdf_by_scale}
	\includegraphics[width=0.8\textwidth]{\figdir/Descriptive/rcdf_by_scale.pdf}
	\caption{
		\textbf{Reverse cumulative-distribution function of mobile authors by geographic scale.}
		\textbf{a.}
		Proportion of mobile authors by how many organizations are represented 	in their career trajectories. 
		For example, for mobile authors, 100 percent of authors held an affiliation with at least two organizations, whereas about 35 percent were affiliated with 3 ore more organizations between 2008 and 2019.
		Mobile authors are defined as those with at least two distinct organizational affiliations represented in our data. 
		\textbf{b.} 68 percent of mobile authors have at least two cities represented in their career trajectories.
		\textbf{c.} 45 percent of mobile authors have 2 or more regions represented in their career trajectories.
		\textbf{d.} Only 14 percent of mobile authors had 2 or more countries represented in their career trajectories. 
	}
\end{figure}

\newpage
%
% Figure - gravity correlation
%
\begin{figure}[hp!]
	\centering
	\label{fig:supp:gravity_correlation}
	\includegraphics[width=\textwidth]{\figdir/GravityLawFig/gravity_correlations.pdf}
	\caption{
		\textbf{Embedding proximity explains more variance for global, within, and between country flux than geographic distance.}
		\textbf{a.}
		Embedding proximity (cosine similarity between vectors) explains more of the total distance than does geographic distance (\textbf{b}). 
		Red line is line of best fit. 
		Black dots are mean flux across binned proximity meas.
		Color indicates frequency of organization pairs within each hex bin.
		Results here are identical to those shown in Fig.~\ref{fig:gravity_performance}a and Fig.~\ref{fig:gravity_performance}.
		\textbf{c-d.}	embedding proximity explains more variance when considering only pairs of organizations within the same country. 
		\textbf{e-f.} embedding proximity more robust than geographic distance for pairs of organizations in different countries. 
	}
\end{figure}

\newpage
\printbibliography{}
